---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FoRecoML

<!-- badges: start -->
[![R-CMD-check](https://github.com/danigiro/FoRecoML/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/danigiro/FoRecoML/actions/workflows/R-CMD-check.yaml) 
[![CRAN status](https://www.r-pkg.org/badges/version/FoRecoML)](https://CRAN.R-project.org/package=FoRecoML) 
`r sprintf("[![devel version](https://img.shields.io/badge/devel version-%s-blue.svg)](https://github.com/danigiro/FoRecoML)", gsub("Version: (.*)", "\\1",  (desc <- readLines("DESCRIPTION"))[grepl("Version", desc, fixed = TRUE)]))`
[![License: GPL-3](https://img.shields.io/badge/license-GPL--3-forestgreen.svg)](https://cran.r-project.org/web/licenses/GPL-3)
<!-- badges: end -->

The goal of FoRecoML is to ...

## Installation

You can install the development version of FoRecoML from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("danigiro/FoRecoML")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(FoRecoML)
## basic example code
```


## Code of Conduct
  
  Please note that the FoRecoML project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
