---
title: "FoRecoML: Nonlinear Forecast Reconciliation with Machine Learning"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FoRecoML}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", eval = FALSE
)
```

## Introduction

FoRecoML extends FoReco with machine learning backends for nonlinear forecast reconciliation
across cross-sectional, temporal, and cross-temporal hierarchies.

## Migration from v1.x to v2.0

### Default backend changed: randomForest → ranger

```{r migration}
# v1.x — old default
# result <- csrml(base, hat, obs, agg_mat)  # used randomForest

# v2.0 — ranger is now the default (faster, equivalent accuracy)
result <- csrml(base, hat, obs, agg_mat)   # uses ranger

# If you need the old default explicitly:
result_rf <- csrml(base, hat, obs, agg_mat, approach = "randomForest")
# ^ This emits a soft deprecation warning
```

## Per-Series vs Global ML

FoRecoML offers two paradigms:

- **Per-series** (`csrml`, `terml`, `ctrml`): one model per bottom-level series.
  Best when series have heterogeneous dynamics.

- **Global** (`csrml_g`, `terml_g`, `ctrml_g`): one model across all series,
  using `series_id` as a categorical feature. Best when series share common patterns
  and `p` is large.

```{r paradigms}
# Per-series (default paradigm)
result_ps <- csrml(base, hat, obs, agg_mat, approach = "ranger")

# Global ML with lightgbm
result_g <- csrml_g(base, hat, obs, agg_mat, approach = "lightgbm")
```

## Normalization Options (normalize_stack)

Global ML benefits from pre-normalizing the feature matrix:

```{r normalization}
# zscore normalization (default in _g wrappers when normalize != "none")
result <- csrml_g(base, hat, obs, agg_mat,
                  approach = "lightgbm",
                  normalize = "zscore")

# Robust normalization with Gini Mean Difference scale
result <- csrml_g(base, hat, obs, agg_mat,
                  approach = "lightgbm",
                  normalize = "robust",
                  scale_fn = "gmd")
```

Available `scale_fn` options: `"gmd"`, `"mad_scaled"`, `"qn"`, `"sn"`, `"iqr_scaled"`, `"sd_c4"`.
The `"qn"` and `"sn"` options require the `robscale` package.

**Zero-scale guard**: Constant series (zero variance) get scale = 1 rather than 0, preventing
division by zero.

## Chunked Incremental Training (batch_size)

For very large hierarchies (large `p`), global models can be trained incrementally:

```{r chunked}
# Auto batch_size: memory-based heuristic
result <- csrml_g(base, hat, obs, agg_mat,
                  approach = "lightgbm",
                  batch_size = "auto")

# Manual batch_size with sequential chunking
result <- csrml_g(base, hat, obs, agg_mat,
                  approach = "lightgbm",
                  batch_size = 100L,
                  chunk_strategy = "sequential")
```

**catboost note**: The catboost R API does not support model continuation (warm-start).
Chunked incremental training is therefore **not supported** for catboost. Use lightgbm
or xgboost for incremental training on large hierarchies.

## Reconciliation Math: sel_mat and agg_mat

The `agg_mat` cross-sectional aggregation matrix maps bottom-level series to aggregate series.
For a hierarchy with 2 aggregate groups and 4 bottom series:

```
agg_mat = | 1 1 0 0 |   (group 1: S1 + S2)
          | 0 0 1 1 |   (group 2: S3 + S4)
```

Post-reconciliation output satisfies: `agg_mat %*% bottom == top` (machine precision).

The internal `sel_mat` (selection matrix) controls which feature columns each series uses.

## Per-Backend Tuning Notes

| Backend | When to use | Categorical series_id |
|---|---|---|
| ranger (default) | Fast, robust, low memory | factor encoding |
| lightgbm | Large hierarchies, incremental training | integer + categorical_feature |
| xgboost | Incremental training, portable models | integer (numeric) |
| mlr3 | Flexible learner selection | factor (auto) |
| catboost | GPU support, categorical data | integer + cat_features |

**Seed reproducibility**: Pass `seed = integer` to any reconciliation function for
reproducible fits. All backends respect `set.seed(seed)` before training.
```
